---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summary.target

<!-- badges: start -->
<!-- badges: end -->

The goal of summary.target is to provide a convenient function for computing the summary statistics for a specific numeric column in a data frame, grouped by one or more specified categorical columns.

The specific summary statistics calculated are as follows:

- Mean

- Minimum

- Maximum

- Standard deviation

## Installation

You can install the development version of summary.target like so:

``` r
# If you haven't install the devtools package, please install it
install.packages("devtools")

#Load the devtools Library
library(devtools)

#If an error occurs say "Loading required package: usethis", then load usethis before load devtools.
library(usethis)

# Then you can install the summary.target package from github
devtools::install_github("stat545ubc-2024/summary.target")
```

## Examples

### This is a basic example which shows you how to solve a common problem:

```{r example}
library(summary.target)
library(datateachr) #To ensure be able to use the dataset steam_games

# The code there summarize the 'discount_price' variable grouped by 'types' in the steam_games dataset.
summarize_target(datateachr::steam_games, "types", "discount_price")
```

### Handling Errors

This function including error handling to check for invalid inputs. For example, if a grouping variable does not exist in the dataset, summary.target will return an informative error message. 
```{r handdling error, error = TRUE}
# Since "color" is not a column in steam_games, it will return an informative error message.
summarize_target(datateachr::steam_games, "color", "discount_price")
```



